Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-12-27 doc/JFLA2022/Slides/Slides.tex
Minor fixes.

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}
    \frametitle{\community}
    \begin{block}{}
      \community is an informal organization that aims to maintain interesting open source \coq projects  andfacilitate collaboration among Coq users on documentation, tooling, etc.
      \begin{itemize}
      \item Created in 2018,  run by volunteer Coq users on GitHub
      \item At present, over than 50 projects, maintained by over than 30 volunteers
      \item Some packages were unmaintained before their integration to \community. According to their scientific or historical interest, we decided to revive them.
        \item After their transfer, packages may be the object of large changes  and refactorings.
      \end{itemize}
    \end{block}
  \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Presenting proofs with \alectr}
\begin{frame}
  \frametitle{Presenting proofs with \alectr}
  \begin{block}{}
    \begin{itemize}
    \item The order in which \coq code; goals and answers are presented in the book is determined by the difficulty of the mathematical examples, or the assumed level in \coq of the reader, not by the structure of the libraries.
    \item
      \emph{\coq libraries contain \emph{snippet declarations} which are converted during the compilation of the book into \LaTeX\xspace blocks which are inserted into the book.}

@@

  \begin{block}{Remarks}
    \begin{itemize}
    \item We could write the book, because we are also the maintainers of the cited \coq source, and could insert the snippet instructions in the \texttt{.v} files. \textcolor{lookcolor}{But what about commenting interesting code from other people (\emph{e.g}
        \gaia) ?}
    \item The same  piece of \coq code may be used in several documents, with different styles (book, beamer), and thus
      different filters (hiding or showing subgoals, hypotheses, etc.).

@@

\begin{frame}[fragile]
  \frametitle{Perspectives}
  \begin{block}{Library on ordinals}
    There exist already \coq libraries which formalize ordinal numbers.
    \begin{itemize}
    \item \gaia (José Grimm) : Formalization of Bourbaki's Elements of Mathematics. {\color{lookcolor}\emph{This library uses an ordinal representation compatible with ours. It is  written in SSreflect/Mathcomp, and is also maintained on \community}.}
    \item A formalization by Minki Cho, using a different representation.
{\color{darkorange}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: 
    forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
}  
    \end{itemize}

@@

\begin{frame}
  \frametitle{More TODOs}
  \begin{block}{}
    \begin{itemize}
    \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item etc.
    \item \Hydras and \community are on github. Please contribute!
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)

>>>>

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}
    \frametitle{\community}
    \begin{block}{}
      \community is an informal organization that aims to maintain interesting open source \coq projects and facilitate collaboration among Coq users on documentation, tooling, etc.
      \begin{itemize}
      \item Created in 2018,  run by volunteer Coq users on GitHub
      \item At present, over than 50 projects, maintained by over than 30 volunteers
      \item Some packages were unmaintained before their integration to \community. According to their scientific or historical interest, we decided to revive them.
        \item After their transfer, packages may be the object of large changes  and refactorings.
      \end{itemize}
    \end{block}
  \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Presenting proofs with \alectr}
\begin{frame}
  \frametitle{Presenting proofs with \alectr}
  \begin{block}{}
    \begin{itemize}
    \item The order in which \coq code, goals and answers are presented in the book is determined by the difficulty of the mathematical examples, or the assumed level in \coq of the reader, not by the structure of the libraries.
    \item
      \emph{\coq libraries contain \emph{snippet declarations} which are converted during the compilation of the book into \LaTeX\xspace blocks which are inserted into the book.}

@@

  \begin{block}{Remarks}
    \begin{itemize}
    \item We could write the book, because we are also the maintainers of the cited \coq source, and could insert the snippet instructions in the \texttt{.v} files. \textcolor{lookcolor}{But what about commenting interesting code from other people (\emph{e.g.},
        \gaia) ?}
    \item The same  piece of \coq code may be used in several documents, with different styles (book, beamer), and thus
      different filters (hiding or showing subgoals, hypotheses, etc.).

@@

\begin{frame}[fragile]
  \frametitle{Perspectives}
  \begin{block}{Library on ordinals}
    There exist already \coq libraries which formalize ordinal numbers.
    \begin{itemize}
    \item \gaia (José Grimm) : Formalization of Bourbaki's Elements of Mathematics. {\color{lookcolor}\emph{This library uses an ordinal representation compatible with ours. It is  written in SSReflect/Mathcomp, and is also maintained in \community}.}
    \item A formalization by Minki Cho, using a different representation.
{\color{darkorange}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: 
    forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
}  
    \end{itemize}

@@

\begin{frame}
  \frametitle{More TODOs}
  \begin{block}{}
    \begin{itemize}
    \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item etc.
    \item \Hydras and \community are on GitHub. Please contribute!
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)
